---
title: "RegressioCovid"
author: "Maksym Rud'"
date: "16 10 2020"
output: html_document
---

```{r setup, include=FALSE}
library(cds)
library(ggplot2)
total_data <- read.csv("Data/owid-covid-data.csv")

france_data <- subset(total_data, location == "France", select = c("date", "new_cases"))
france_data$date <- as.numeric(france_data$date)
france_data <- france_data[c(150:nrow(france_data)),]
for(i in c(1:nrow(france_data))){
  if(france_data[i,2] < 0){
    france_data[i,2] <- abs(france_data[i,2])
  }
  else if(france_data[i,2] == 0){
    france_data[i,2] <- 1
  }
}



knitr::opts_chunk$set(echo = TRUE)
```

## Regression Model

Let's investigate our model to check if it has any paticular pattern.
```{r cars}

plot(france_data$date, france_data$new_cases, main="Each day new cases changes",
     xlab="Day", ylab="New Corona Virus Cases")
```

Curve of observations seems like an exponential pattern of growth. 

Let's esume that this model has nonlinear model like.

$$y = \alpha e^{\beta x}$$

$$log(y) = log(\alpha) + \beta x $$


But before implementing this method we should find suitable starting values for our estimates. I used linear model for estimating


## Finding right starting values

```{r pressure}
model.0 <- lm(log(new_cases) ~ date, data=france_data)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

startval <- list(alpha = alpha.0, beta = beta.0)
startval
```

## Using Non-linear Least squares method


```{r fittingmodel}

model <- nls(new_cases ~ alpha * exp(beta*date), data=france_data, start = startval)

plot(france_data$date, france_data$new_cases, main="Fitting Exponential",
     xlab="Day", ylab="New Corona Virus Cases")
lines(france_data$date, predict(model, list(x = france_data$date)), col = 'red', lwd =3)
```


It seems like a suitable model for our data. Steel we need to check if the tale didn't ruined everything

## Residual Plots

```{r res}
data.res <- residuals(model)
plot(france_data$new_cases, data.res, xlab = "New_cases", ylab = "Residuals", main = "Residuals vs fit plot")
```

```{r respred}
data.res <- residuals(model)
plot(france_data$date, data.res, xlab = "Date", ylab = "Residuals", main = "Residuals vs predictor plot")
```

## Q-Q plot residuals

```{r resqq}
qqnorm(data.res, ylab="Standardized Residuals", xlab="Normal Scores", main="Covid-19 cases")

```



## Measuring a fit

```{r measfit}
(RSS.p <- sum(residuals(model)^2))
(TSS <- sum((france_data$new_cases - mean(france_data$new_cases))^2)) 
1 - (RSS.p/TSS)  # R-squared measure
```

As we can see may be we should better use polinomial function

## Log of our Data
```{r plotting}
plot(france_data$date, log(france_data$new_cases), main="Each day new cases changes logged",
     xlab="Day", ylab="New Corona Virus Cases")
```
Let's esume...

$$ log(y) = \beta_1x$$
where $x$ is our date



## Fitting polinomial model

```{r plmod}
model.lm <- lm(log(new_cases) ~ date, data = france_data)
```


## Fitting on a plot

```{r fitplot}
plot(france_data$date, log(france_data$new_cases), main="Fitting Polynomial",
     xlab="Day", ylab="New Corona Virus Cases")
lines(france_data$date, predict(model.lm, data=france_data), col = 'red', lwd = 2)

```

## Residual Plots

### Seventh Polynom

```{r resid7}
data.res <- residuals(model.lm)
plot(log(france_data$new_cases), data.res, xlab = "New_cases", ylab = "Residuals", main = "Residuals poly7 vs fit plot")
```

```{r respred7}
data.res <- residuals(model.lm)
plot(france_data$date, data.res, xlab = "Date", ylab = "Residuals", main = "Residuals poly7 vs predictor plot")
```

## Q-Q plot residuals

```{r resq}
qqnorm(data.res, ylab="Standardized Residuals", xlab="Normal Scores", main="Covid-19 cases")

```
## Measuring a fit

### Seventh

```{r measfitpoly7}
(RSS.p <- sum(residuals(model.lm)^2))
(TSS <- sum((france_data$new_cases - mean(france_data$new_cases))^2)) 
1 - (RSS.p/TSS)  # R-squared measure
```

After all we create a approximate model of our data 