---
title: "Correlation"
author: "Maksym Rud'"
date: "27 09 2020"
output: pdf_document
---
# Correlation Analysis
## Europe 2016 data_set

```{r setup, include=FALSE}

library(psych)
library(corrplot)
library(corrr)

data_crime <- read.csv("Europe/crime_2016.csv")
data_gdp <- read.csv("Europe/gdp_2016.csv")
data_life_expectancy <- read.csv("Europe/life_expectancy_2016.csv")
data_low_savings <- read.csv("Europe/low_savings_2016.csv")
data_work_hours <-read.csv("Europe/work_hours_2016.csv")

total <- merge(data_crime, data_gdp, by="country")
total <- merge(total, data_life_expectancy , by = "country")
total <- merge(total, data_low_savings , by = "country")
data_europe <- merge(total, data_work_hours, by = "country")


knitr::opts_chunk$set(echo = TRUE)
```

## Data
```{r data}
head(data_europe)
```

## Matrix plot

### Pearson matrix plot
```{r matrixplot}
pairs.panels(data_europe[,2:6], 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )

```

## Corr Plot

```{r corrplot, echo=FALSE}
EU <- cor(data_europe[,2:6])
corrplot(EU, method ="circle")
```

### Cluster

```{r corrplot2, echo=FALSE}
EU <- cor(data_europe[,2:6])
corrplot(EU, method ="shade", order="hclust")
```

## Graph plot

```{r graphplot}
network_plot(EU)
```

## Tests for percent of low savings and avg hours of work

```{r test1}
res <- cor.test(data_europe$avg_hrs_worked, data_europe$prct_low_savings, method = "pearson")
res
```

### The p-value of the test is  0.003338, which is less than the significance level alpha = 0.05. We can conclude that low savings and avg hours of work are significantly correlated with a correlation coefficient of 0.503076 and p-value of 0.003338 .

```{r test12, warning=FALSE}
res <- cor.test(data_europe$avg_hrs_worked, data_europe$prct_low_savings, method = "spearman")
res
```

```{r test13, warning=FALSE}
res <- cor.test(data_europe$avg_hrs_worked, data_europe$prct_low_savings, method = "kendall")
res
```

## Tests for percent of low savings and life excpectations

```{r test2}
res <- cor.test(data_europe$life_expect, data_europe$prct_low_savings, method = "pearson")
res
```

### The p-value of the test is   0.0002015, which is less than the significance level alpha = 0.05. We can conclude that low savings and life excpectations are significantly correlated with a correlation coefficient of -0.6113428 and p-value of 0.0002015.

```{r test3, warning=FALSE}
res <- cor.test(data_europe$life_expect, data_europe$prct_low_savings, method = "spearman")
res
```

```{r test4, warning=FALSE}
res <- cor.test(data_europe$life_expect, data_europe$prct_low_savings, method = "kendall")
res
```



