---
  
title: "BasicStatistic"
author: "Maksym Rud'"
date: "13 09 2020"
output: pdf_document
  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(e1071)
library(nortest)
library(circular)
nsim <- function(n, m = 0, s = 1) {
    z <- rnorm(n)
    m + s * ((z - mean(z)) / sd(z))
}

nboot <- function(x, R) {
    n <- length(x)
    m <- mean(x)
    s <- sd(x)
    do.call(rbind,
            lapply(1 : R,
                   function(i) {
                       xx <- sort(nsim(n, m, s))
                       p <- seq_along(x) / n - 0.5 / n
                       data.frame(x = xx, p = p, sim = i)
    }))
}

```

## Father's Hight Statistics

The table below gives the heights of fathers and their sons, based on a famous experiment by Karl Pearson around 1903. The number of cases is 1078. Random noise was added to the original data, to produce heights to the nearest 0.1 inch.

```{r fathers}
my_data <- read.delim(file.choose())

knitr::kable(head(my_data[1:5,]), "simple")
```

Here are some basic evaluations of the data

```{r f.stat}

print(c("Mean", mean(my_data$Father)))

print(c("Median", median(my_data$Father)))

print(c("Variance", var(my_data$Father)))

print(c("Standart deviation", sd(my_data$Father)))

print(c("coef of variance", sd(my_data$Father)/mean(my_data$Father)))

print(c("Range of the set of data", max(my_data$Father) - min(my_data$Father)))

print(c("interquartile range", IQR(my_data$Father, na.rm = FALSE)))


```

## Box Plot

The plot is representing interquartile range, mean and "vityk" values and informal information about density distribution.

```{r ploting}

ggplot(my_data) +
  aes(y = unlist(my_data[2])) +
  geom_boxplot() +
  coord_flip() +
  labs(
    y = "heights"
  )
```

## Quartiles

```{r quartiles}

quantile(my_data$Father)

```

## Summary

```{r charct}

summary(my_data$Father)

```

## First and Ninth Deciles

```{r deciles}
quantile(my_data$Father, prob = seq(0, 1, length = 11), type = 5)[2]
quantile(my_data$Father, prob = seq(0, 1, length = 11), type = 5)[10]

```

## Skewness

```{r skewness}

skewness(my_data$Father)

```

## Kurtosis

```{r kurtosis}

kurtosis(my_data$Father)

```

## Histograms based on 

```{r stand_gist}

hist(my_data$Father, main = "Standart rule", xlab = "height", freq = FALSE)
std = sqrt(var(my_data$Father))
curve(dnorm(x,mean = mean(my_data$Father), sd = std), add = TRUE, col="red")

```


```{r sturge}

hist(my_data$Father, main = "Sturges rule", xlab = "height", ylim = c(0, 200))

```


```{r Freedman-Diaconis}

hist(my_data$Father,main = "Freedman-Diaconis rule", xlab = "height", breaks = "FD", freq = FALSE, 
     xlim = c(56, 76), ylim = c(0, 0.2))
curve(dnorm(x,mean = mean(my_data$Father), sd = std), col="red", add = TRUE)

```

```{r Scotts, warning=FALSE}

hist(my_data$Father,main = "Scott's rule", xlab = "height",  breaks = "Scott", freq = FALSE, xlim = c(56, 76))
curve(dnorm(x,mean = mean(my_data$Father), sd = std), col="red", add = TRUE)


```

## Creating a Normal Quantile–Quantile Plot

Sometimes it’s important to know if your data is normally distributed. A quantile–quantile (Q–Q) plot is a good first check.

```{r qq}

ggplot(my_data, aes(sample = Father)) +
  stat_qq() +
  stat_qq_line() +
  labs(title = "Q-Q normal plot for father's hights")

```

If the data had a perfect normal distribution, then the points would fall exactly on the diagonal line. Many points are close, especially in the middle section in particular.

##  Creating a Normal Probability-Probability plot

```{r pp}

m <- mean(my_data$Father)
s <- sd(my_data$Father)
n <- nrow(my_data)
p <- (1 : n) / n - 0.5 / n
gb <- nboot(my_data$Father, 50)
pp <- ggplot() +
geom_line(aes(x = p, y = pnorm(x, m, s), group = sim),
          color = "gray", data = gb)
pp + 
geom_point(aes(x = p, y = sort(pnorm(Father, m, s))), data = (my_data))

```

## Shapiro, Anderson-Darling, Cramer-von Mises, Pearson chi-square, Kolmogorov normality test

```{r test, warning=FALSE}

shapiro.test(my_data$Father)

ad.test(my_data$Father)

cvm.test(my_data$Father)

pearson.test(my_data$Father)

ks.test(x = my_data$Father, y = pnorm(nrow(my_data), m, s))
```


